Robust positively invariant sets for state dependent and scaled disturbances

### 2015-03-21 draft.tex
Made my changes.

In many applications we are interested in the largest such set, denoted $\mathcal X^\infty$, which is given 
by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$. This set is known as the maximal robust 
positively invariant (MRPI) set and has been used extensively, for example, to define terminal regions in 
robust model predictive control~\cite{mayne:2000}. Although analytical properties
of these sets were derived at the time of their introduction, algorithms for numerically computing MRPI sets 
were introduced much later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}. 
%\note{You commented 'check', I didn't know what that meant.}
Earlier algorithms did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, 
or were not guaranteed to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
%
However for the case of disturbances belonging to a fixed set $\mathscr V$, methods of computing 
$\mathcal X^\infty$ are now well established~\cite{blanchini:2007}.

This paper considers sets of disturbances that depend on
parameters. First we consider state-dependent sets,
\begin{equation}\label{eq:PWA:disturbance:set}
	\mathcal V(x) = \left\{v: Gv\leq H(x)\right\},
\end{equation}
where $G$ is a real matrix,
%$G\in\mathbb R^{n_G\times n_v}$, 
$H(x)$ is a convex piecewise affine function, and the inequality applies elementwise. For the case that $\mathscr V=\mathcal V(x)$ we
provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss 
computation of $\mathcal X^\infty$. The case of disturbances depending on states (or control inputs) 
is considered in~\cite{Kuntsevich:1995,rakovic06} but the convexity
analysis of this paper and the associated computational approach are novel. 
State dependent disturbance constraints can account for linearisation errors, as shown in section~\ref{sec:first:example}, 
as well as more general multiplicative parametric model uncertainty.

The second case considered is that of scaled disturbance sets of the form
\begin{equation}
  \mathcal V(\theta) = \{v:Gv\leq(1+\theta){\bf{1}}\},
\end{equation}
for scalar $\theta>-1$. For $\mathscr V = \mathcal V(\theta)$ we compute sets $\mathcal Z^\infty$ in 
$(x\times\theta)$-space with the property that 
% To distinguish the resulting sets from regular MRPI sets we use $\mathcal Z^\infty$
% to emphasise that $\mathcal Z^\infty$ 
the intersection, $\mathcal Z^\infty\vert_{\hat\theta}$, with the subspace on which $\theta=\hat\theta$ 
for given $\hat\theta$ is an MRPI set. To our best knowledge, this setup has not been 
considered in the literature. This type of disturbance constraint can be used to study the sensitivity of
the MRPI set to changes in the disturbance \emph{strength}.

@@

Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets. For sets $\mathcal A, \mathcal B \subset\mathbb R^n$, the Minkowski set addition is denoted $\mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}$.
We use ${\bf{1}}$ to denote the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 

@@

This section discusses sets that depend on a parameter such as the state of \eqref{eq:system:equation} (so called point-to-set maps, 
see~\cite{Hogan:1973}), and extends the existing set algebra~\cite{blanchini:2007} to 
accommodate such sets. We present the general case first, then illustrate it with the example of a pointwise polyhedral set in the form of (\ref{eq:PWA:disturbance:set})
% with piecewise affine $H(x)$.

@@

% In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
%       \begin{equation}
%         \mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}.
%       \end{equation}

@@

\[%      \begin{equation}

@@

\]%      \end{equation}

@@

      convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies
    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$).

@@

    % \begin{thm}\label{thm:convex:parametric:set}
    %   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:disturbance:set} for a function $H(x)$ that is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~each element $H_i(x)$ of $H(x)$ satisfies
    % $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$) is parametrically 
    %   convex for all $x\in \mathcal X$.
    % \end{thm}

@@

      To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq 
      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ and $x_1, x_2\in\mathcal X$ we note that

@@

% Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
% and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
% the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.
% Furthermore, we will see that if $\mathcal X$ is polytopic and $\mathcal 
% V(x)$ is pointwise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
% again a polytopic set. This will become more clear in the next section when we describe 
% the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
and~\ref{thm:convex:parametric:set} imply that, if $\mathcal V(x)$ is defined by \eqref{eq:PWA:disturbance:set} in terms of an elementwise convex function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$

@@

%This will become more clear in the next section when we describe 
%the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.

@@

In this section we describe an iterative algorithm to compute the MRPI 
set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbances
$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined by~\eqref{eq:PWA:disturbance:set} with a piecewise affine function $H(x)$.

@@

%\note{is it necessary to assume that $\mathcal V(x)$ is bounded $\forall x\in\mathcal X_0$?}

@@

%\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
%So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}
by iteratively introducing
constraints that exclude all points for which the successor state can lie outside 

@@

\[%\begin{equation}

@@

\]%\end{equation}

@@

but is the solution of a multiparametric linear program and hence will be given 

@@

%\begin{equation}

@@

	 = \begin{array}[t]{rl} \displaystyle\max_v & \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array} \\
	 &= \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}

@@

%\end{equation}

@@

In closed form the iterates can be expressed (assuming for convenience that $\Psi$ is invertible) as

@@

	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{0 \leq i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).

@@

-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined by~\eqref{eq:PWA:disturbance:set}
in terms of a piecewise affine function $H(x)$.
Then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty 
=\mathcal X_N$ is a polytope.

@@

From~\eqref{eq:set:iteration:state:dependent:constraints} it is clear that $\mathcal X^\infty = \emptyset$ if $\mathcal X_k =\emptyset$ for any $k\geq 0$.
%Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early iterations the parametric Pontryagin difference can yield the empty set. The empty set however is an admissible polytope, i.e. an admissible MRPI set. 
For the remainder of the proof we assume
that the MRPI set $\mathcal X^\infty$ is non-empty. For this we require that $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact on any compact set $\mathcal S\subset\mathbb R^n$.

@@

For the first step, notice that observability of
$(\Psi,\Gamma)$ is equivalent to the observability matrix $\Omega$ having full rank, i.e.\ $\mathrm{rank}(\Omega) = \mathrm{rank}(\begin{bmatrix} \Gamma^T \ \cdots \ (\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
% \[
% \Omega = \left(\begin{array}{c}
% \Gamma\\ \vdots \\ \Gamma\Psi^{n-1}
% \end{array}\right)
% \]
%having a trivial kernel. 

@@

the set $\mathcal X_{n}$ is also bounded. 
%The case that  $N<n$ can occur if $\mathrm{rank}(\Gamma) > 1$.
%More generally, to 
To show that $D_k$ grows exponentially we use the compactness of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let

@@

be the biggest ball that is contained in $\mathcal X_{0}$. From~\eqref{eq:set:iteration:state:dependent:constraints}, $D_k$ has the representation

@@

Since $\Psi$ is asymptotically stable we have $\rho<1$ and therefore
$\rho^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$,
implying exponential growth of $D_k$ provided $\mathcal S_2$ is bounded. 
%Recall that we assume
%However the MRPI set is non-empty by assumption, and t
To bound $\mathcal S_2$ we note that for $k\geq n$ we have $\mathcal S_2\subseteq \bigoplus_{0\leq i\leq k-1} \rho^i K_2 \subseteq
\frac{1}{1-\rho} K_2$.
Thus $D_k$ grows exponentially,
whereas $\mathcal X_k$ is contained in a ball of
finite radius, and hence we conclude from \eqref{eq:set:iteration:state:dependent:constraints} that 

@@

%after a finite number of iterations $N$ intersecting with $D_{N+1}$
%will no longer change $\mathcal X_N$.

@@

In this section we discuss the calculation of the MRPI set for a linearised simplified model of the magnetic levitation system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given

@@

$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot
y)^T$. We find that any equilibrium has $\dot{y}=0$ and
$u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$.
Linearising the nonlinear differential equation $\dot x = f(x,u)$
around an equilibrium point $(\hat x, \hat u)$ 
%such that $f(\hat x,\hat u) = 0$, 
gives the approximate model 

@@

@@

linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$

@@

%+ A \tilde x + B \tilde u - A \tilde x - B\tilde u\\

@@

$H^x$ and $H^u$ can be determined by integration. Suppose that
for $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact
sets, the values of $H^x$ and $H^u$ are known, i.e.\
$H^x\tilde x+H^u\tilde u\in\conv_k\{H^x_k\tilde x + H^u_k\tilde u\}$ for all $(\tilde x,\tilde u)\in\mathcal X\times \mathcal U$.

@@

In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation} with a disturbance set parametrised by a scalar $\theta$:

@@

solving multiparametric linear programs in every step of the proposed iteration.

@@

The set $\mathcal V(\theta)$ is nonempty and contains the origin for all $\theta>-1$ and hence the 

@@

%\\
%&\theta>-1

@@

is positive for any nonzero $c$.

@@

$\mathcal Z = \{(x,\theta):\mathcal F_i x+\mathcal G_i\theta \leq 1,\forall\, i\leq m\}$.

@@

	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \ \forall\, v\in\mathcal V(\theta), \ i\leq m\}\\

@@

	 + \mathcal G_i \theta \leq 1 \ \forall\, i\leq m\Biggr\}\\

@@

	 + \mathcal G_i \theta \leq 1 \ \forall\, i\leq m\Biggr\}\\
	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \ \forall \, i\leq m

@@

	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\leq m\biggr\}

@@

we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band: $\mathcal Z\vert_{\hat\theta}=\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}\subseteq
\mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the following result.

@@

%\note{You wrote to highlight $\mathcal V(0)$ being bounded was an assumption. It is necessary so I don't know what to do with this.}

@@

The iterative process described above allows uniform scaling of the disturbance set. As mentioned earlier, the algorithm can be extended to the case of non-uniformly scaled input constraints to accommodate more degrees of freedom for 
system analysis simply by using 
\[
\mathcal Z = \{(x,\theta,\alpha): \mathcal F x + \mathcal G\theta + 
\mathcal H \alpha \leq {\bf{1}}\}.
\]
This does not affect the algorithm since at each step of the iteration 
the elements of $\mathcal H$ remain unchanged. 
%In the next section we will illustrate the algorithm.
%
%
%
%
%
%
\section{Examples}\label{sec:second:example}
%
%
In this section we compute MRPI sets for the levitating ball system presented in 
section~\ref{sec:first:example} and for a purely numerical model. These examples illustrate the effectiveness of the proposed approach for state dependent disturbances and the use of parametrised MRPI sets as a system analysis tool.

First we present the parametrised MRPI
set for the levitating ball. To obtain results comparable to those in Section~\ref{sec:first:example} we derive fixed bounds
on the effect of nonlinearities on each state by finding a fixed set containing the set $\mathcal V(x,u)$ 
in~\eqref{eq:definition:element:wise:constraints:on:nonlinearities} for all $(x,u)\in\mathcal X\times\mathcal U$. 
%Using the same constraint set $\mathcal X \times \mathcal U$ to determine 
This yields a constant set $\mathcal V$ which is non-symmetric around the origin due to nonlinearity. We also introduce
a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$ for $\alpha=0$. For this setup we obtain the MRPI
set $\mathcal Z^\infty=\{(x,\theta,\alpha): \Lambda_i^x x + \Lambda_i^\theta \theta + \Lambda_i^\alpha \alpha\leq
\lambda_i\,\forall i\leq m_\infty\}$. Notice that since $\alpha$ was introduced as a scaling parameter
for $\mathcal U(\alpha)=\{u: Fu\leq (1+\alpha){\bf{1}}\}$ all entries in $\mathcal H$ are non positive and
remain unchanged throughout the computation of $\mathcal Z^\infty$ so that $\Lambda^\alpha$ has only non
positive entries, i.e. increasing $\alpha$ will enlarge the parametrised MRPI set $\mathcal Z^\infty\vert_{\alpha_1}
\subseteq\mathcal Z^\infty\vert_{\alpha_2}$ for $\alpha_1\leq\alpha_2$.

>>>>

In many applications we are interested in the largest such set, denoted $\mathcal X^\infty$, which is given 
by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$. This set is known as the maximal robust 
positively invariant (MRPI) set and has been used extensively, for example, to define terminal regions in 
robust model predictive control~\cite{mayne:2000}. Although analytical properties
of these sets were derived at the time of their introduction, algorithms for numerically computing MRPI sets 
were introduced much later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}. 
Earlier algorithms did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, 
or were not guaranteed to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
%
However for the case of disturbances belonging to a fixed set $\mathscr V$, methods of computing 
$\mathcal X^\infty$ are now well established~\cite{blanchini:2007}.

This paper considers sets of disturbances that depend on
parameters. First we consider state-dependent sets,
\begin{equation}\label{eq:PWA:disturbance:set}
	\mathcal V(x) = \left\{v: Gv\leq H(x)\right\},
\end{equation}
where $G$ is a real matrix,
$H(x)$ is a convex piecewise affine function, and the inequality applies elementwise. For the case that $\mathscr V=\mathcal V(x)$ we
provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss 
computation of $\mathcal X^\infty$. The case of disturbances depending on states (or control inputs) 
is considered in~\cite{Kuntsevich:1995,rakovic06} but the convexity
analysis of this paper and the associated computational approach are novel. 
State dependent disturbance constraints can account for linearisation errors, as shown in section~\ref{sec:first:example}, 
as well as more general multiplicative parametric model uncertainty.

The second case considered is that of scaled disturbance sets of the form
\begin{equation}
  \mathcal V(\theta) = \{v:Gv\leq(1+\theta){\bf{1}}\},
\end{equation}
for scalar $\theta>-1$. For $\mathscr V = \mathcal V(\theta)$ we compute sets $\mathcal Z^\infty$ in 
$(x\times\theta)$-space with the property that 
the intersection, $\mathcal Z^\infty\vert_{\hat\theta}$, with the subspace on which $\theta=\hat\theta$ 
for given $\hat\theta$ is an MRPI set. To our best knowledge, this setup has not been 
considered in the literature. This type of disturbance constraint can be used to study the sensitivity of
the MRPI set to changes in the disturbance \emph{strength}.

@@

Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half 
spaces as polyhedra, and to bounded polyhedra as polytopic sets. For sets $\mathcal A, \mathcal B 
\subset\mathbb R^n$, the Minkowski set addition is denoted $\mathcal A\oplus\mathcal B = \{c : c = a + 
b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}$. We use ${\bf{1}}$ to denote the column vector of ones 
in appropriate dimensions, and $\wedge$ is the logical AND operator, index sets are denoted by $\mathcal I
\subset\mathbb N$. 

@@

This section discusses sets that depend on a parameter such as the state of \eqref{eq:system:equation} 
(so called point-to-set maps, see~\cite{Hogan:1973}), and extends the existing set algebra~\cite{blanchini:2007} to 
accommodate such sets. We present the general case first, then illustrate it with the example 
of a pointwise polyhedral set in the form of (\ref{eq:PWA:disturbance:set})

@@

@@

@@

@@

  convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset 
  \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies $H_i(\lambda x_1+(1-\lambda)x_2)\leq 
  \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$).

@@

@@

To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq \lambda\mathcal V(x_1) \oplus(1-\lambda)
\mathcal V(x_2)$ for all $\lambda \in [0,1]$ and $x_1, x_2\in\mathcal X$ we note that

@@

Lemmas~\ref{thm:convexity:of:pontryagin:difference} and~\ref{thm:convex:parametric:set} imply that, 
if $\mathcal V(x)$ is defined by \eqref{eq:PWA:disturbance:set} in terms of an elementwise convex 
function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$

@@

@@

In this section we describe an iterative algorithm to compute the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent} 
for a linear system~\eqref{eq:system:equation} subject to disturbance
$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined 
by~\eqref{eq:PWA:distrubance:set} with a convex piecewise affine $H(x)$.
Notice that the set $\mathcal V(x)$ is pointwise polytopic set~\eqref{eq:definition:MRPI:set:state:dependent} 
for a linear system~\eqref{eq:system:equation} subject to disturbances
$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined 
by~\eqref{eq:PWA:disturbance:set} with a convex piecewise affine function $H(x)$.

@@

@@

by iteratively introducing constraints that exclude all points for which the successor state can lie outside 

@@

@@

@@

but is the solution of a multi-parametric linear program and hence will be given 

@@

@@

	 = \begin{array}[t]{rl} \displaystyle\max_v & \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)
   \end{array} \\ 
   &= \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in 
   \Psi^{l-1}\mathcal V(x) \end{array}

@@

@@

In closed form the iterates can be expressed as
\note{We actually do NOT assume that $\Psi$ is invertible! We don't need its inverse at any point! $\Psi^{-1}$ appears only
in this closed form representation but it merely denotes the preimage of $\mathcal X_k$ because that is all we need that the preimages
keep growing. It might be confusing with the notation but that is only to emphasise that it behaves like the inverse..}

@@

	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{0 \leq i\leq l-1}{\bigominus} 
  \Psi^i \mathcal V(\mathcal X_{l-1})\right).

@@

-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined 
by~\eqref{eq:PWA:disturbance:set} in terms of a piecewise affine function $H(x)$. Then $\mathcal X_N\subseteq \mathcal 
X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty =\mathcal X_N$ is a polytope.

@@

From~\eqref{eq:set:iteration:state:dependent:constraints} it is clear that $\mathcal X^\infty = \emptyset$ 
if $\mathcal X_k =\emptyset$ for any $k\geq 0$. For the remainder of the proof we assume that the MRPI set 
$\mathcal X^\infty$ is non-empty. For this we require that $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is 
compact on any compact set $\mathcal S\subset\mathbb R^n$.

@@

For the first step, notice that observability of $(\Psi,\Gamma)$ is equivalent to the observability matrix 
$\Omega$ having full rank, i.e.\ $\mathrm{rank}(\Omega) = \mathrm{rank}(\begin{bmatrix} \Gamma^T \ \cdots \ 
(\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
\note{This looks very MATLAB.. I don't like it.}

@@

the set $\mathcal X_{n}$ is also bounded. To show that $D_k$ grows exponentially we use the compactness 
of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let

@@

be the biggest ball that is contained in $\mathcal X_{0}$. From~\eqref{eq:set:iteration:state:dependent:constraints}, 
$D_k$ has the representation

@@

Since $\Psi$ is asymptotically stable we have $\rho<1$ and therefore $\rho^{-l}K_1\subseteq\Psi^{-l} K_1 
\subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$, implying exponential growth of $D_k$ provided $\mathcal S_2$ 
is bounded. To bound $\mathcal S_2$ we note that for $k\geq n$ we have $\mathcal S_2\subseteq 
\bigoplus_{0\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 
$\mathcal X_k$ is contained in a ball of finite radius, and hence we conclude from~\eqref{eq:set:iteration:state:dependent:constraints} that 

@@

@@

In this section we discuss the calculation of the MRPI set for a linearised simplified model of the magnetic 
levitation system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given

@@

$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that any equilibrium has 
$\dot{y}=0$ and $u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$. Linearising the nonlinear differential 
equation $\dot x = f(x,u)$ around an equilibrium point $(\hat x, \hat u)$ gives the approximate model 

@@

\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer $=$ since we 
will take it as an equality after all not handling discretisation errors at all..}

@@

linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ 
with $V(x)=x^T P x\geq0$, i.e. $x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$

@@

@@

where $H^x$ and $H^u$ can be determined by integration. 
Suppose that for all $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact sets,
we can bound the values of $H^x x+ H^u u$ by a finite convex combination of extremal values, i.e. 
$H^x x+H^u u\in\conv_k\{H^x_k x + H^u_k u\}$.
\note{I did't like this passage. It made it seem obvious that the nonlinearities are contained in a polytope spanned by
extremal values.. That's obviously not the case..}

@@

In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation} with a disturbance set 
parametrised by a scalar $\theta$:

@@

solving multi-parametric linear programs in every step of the proposed iteration.

@@

The set $\mathcal V(\theta)$ is non-empty and contains the origin for all $\theta>-1$ and hence the 

@@

@@

is positive for any non-zero $c$.

@@

$\mathcal Z = \{(x,\theta):\mathcal F_i x+\mathcal G_i\theta \leq 1,\forall\, i\in\mathcal I\}$.

@@

	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \ \forall\, v\in\mathcal V(\theta), \ i\in\mathcal I_0\}\\

@@

	 + \mathcal G_i \theta \leq 1 \ \forall\, i\in\mathcal I_0\Biggr\}\\

@@

	 + \mathcal G_i \theta \leq 1 \ \forall\, i\in\mathcal I_0\Biggr\}\\
	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \ \forall \, i\in\mathcal I_0

@@

	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\in\mathcal I_0\biggr\}

@@

we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band: $\mathcal Z\vert_{\hat\theta}
=\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}\subseteq \mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma 
x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the following result:

@@

@@

The iterative process described above allows uniform scaling of the disturbance set. As mentioned earlier, the 
algorithm can be extended to the case of non-uniformly scaled input constraints to accommodate more degrees of freedom for 
system analysis simply by using 
%
\[
\mathcal Z = \{(x,\theta,\alpha): \mathcal F x + \mathcal G\theta + 
\mathcal H \alpha \leq {\bf{1}}\}.
\]
%
This does not affect the algorithm since at each step of the iteration 
the elements of $\mathcal H$ remain unchanged. 
%
%
%
%
%
%
\section{Examples}\label{sec:second:example}
%
%
In this section we compute MRPI sets for the levitating ball system presented in 
section~\ref{sec:first:example} and for a purely numerical model. These examples illustrate the effectiveness 
of the proposed approach for state dependent disturbances and the use of parametrised MRPI sets as a system analysis tool.

First we present the parametrised MRPI
set for the levitating ball. To obtain results comparable to those in Section~\ref{sec:first:example} we derive fixed bounds
on the effect of nonlinearities on each state by finding a fixed set containing the set $\mathcal V(x,u)$ 
in~\eqref{eq:definition:element:wise:constraints:on:nonlinearities} for all $(x,u)\in\mathcal X\times\mathcal U$. 
This yields a constant set $\mathcal V$ which is non-symmetric around the origin due to nonlinearity. We also introduce
a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$ for $\alpha=0$. For this setup we obtain the MRPI
set $\mathcal Z^\infty=\{(x,\theta,\alpha): \Lambda_i^x x + \Lambda_i^\theta \theta + \Lambda_i^\alpha \alpha\leq
\lambda_i\,\forall i\leq m_\infty\}$. Notice that since $\alpha$ was introduced as a scaling parameter
for $\mathcal U(\alpha)=\{u: Fu\leq (1+\alpha){\bf{1}}\}$ all entries in $\mathcal H$ are non positive and
remain unchanged throughout the computation of $\mathcal Z^\infty$ so that $\Lambda^\alpha$ has only non
positive entries, i.e. increasing $\alpha$ will enlarge the parametrised MRPI set $\mathcal Z^\infty\vert_{\alpha_1}
\subseteq\mathcal Z^\infty\vert_{\alpha_2}$ for $\alpha_1\leq\alpha_2$.

First we compare the MRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
constraints with the parametrised set $\mathcal Z^\infty$. To do this we compute the scaling parameter 
$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\theta=0,\alpha=\alpha_{\min})}$
by solving $m_\infty$ linear programs
%
%
\[
	\gamma_i^\ast = \begin{aligned}[t]
	\max_x & \ \Lambda_i^x x\\
	\text{s.t.}& \ x\in\mathcal X^\infty
	\end{aligned}
\]
%
%
The minimal value for $\alpha_{\min}$ is then given by the maximal $\alpha$ satisfying $\gamma_i^\ast + 
\Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. Solving this we obtain the 
minimal value $\alpha_{\min} = 1.7555$ and the MRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:MRPIs}.
The computation terminates after seven iterations and produces a polyhedron $\mathcal Z^\infty$ supported by $m_\infty=10$
planes.
Caution is advised when interpreting $\alpha>0$, since the system is nonlinear.
extrapolations reveal little insight, however $\alpha_{\min} > 0$ indicates that the current set of inputs $\mathcal U(0)=\mathcal U$ 
is not large enough to cope with the perturbation set given by upper bounds of the nonlinear effects.
%
%
\begin{figure}
\begin{lpic}{minimalAlphaForConstantDisturbance(.65,)}
{\tiny
\lbl[r]{7,87;$1.5$}
\lbl[r]{7,69;$1$}
\lbl[r]{7,51;$0.5$}
\lbl[r]{7,34;$0$}
\lbl[r]{7,16;$-0.5$}
\lbl[t]{15,2;$-0.06$}
\lbl[t]{27,2;$-0.05$}
\lbl[t]{39,2;$-0.04$}
\lbl[t]{51,2;$-0.03$}
\lbl[t]{63,2;$-0.02$}
\lbl[t]{75,2;$-0.01$}
\lbl[t]{89,2;$0$}
\lbl[t]{100,2;$0.01$}
\lbl[t]{113,2;$0.02$}
}
{\footnotesize
\lbl[r]{5,45,90;$\tilde x_2$}
\lbl[t]{121,3;$\tilde x_1$}
}
\lbl[l]{93,32;$\longleftarrow\mathcal X^\infty$}
\lbl[r]{68,43;$\mathcal Z^\infty\vert_{(0,\alpha_{\min})}\longrightarrow$}
\end{lpic}
\caption{The minimal scaling of the constant disturbance set such that the associated MRPI set contains
the MRPI set for piecewise affine disturbances is $\alpha_{\min}=1.7555$. Note that since the nonlinearities of the system
 dynamics are not symmetrical around the equilibrium the MRPI set with fixed constraints on the disturbance
 is non-symmetric.}
 \label{fig:minimal:scaling:comparison:MRPIs}
\end{figure}
